### 2015-05-13 evaluation.tex
fix
update

\whoop uses over-approximation to achieve scalability and, as expected, executes significantly faster than \corral in all our benchmarks. For example, \corral times out in all configurations (without and without \whoop) when trying to analyze the r8169 ethernet driver, while \whoop manages to analyze the driver in 144.5 seconds. We believe that the reason behind this is that r8169 has deeply-nested recursion in some entry points, which might get \corral stuck. This is not an issue for \whoop, which uses procedure summarization. This shows that \whoop has value as a stand-alone analyzer.

@@

>>>>

\whoop uses over-approximation to achieve scalability and, as expected, executes significantly faster than \corral in all our benchmarks. For example, \corral times out in all configurations (without and without \whoop) when trying to analyze the r8169 ethernet driver, while \whoop manages to analyze the driver in 144.5 seconds. We believe that the reason behind this is that r8169 has deeply-nested recursion in some of its entry points, which might get \corral stuck. This is not an issue for \whoop, which uses procedure summarization. This shows that \whoop has value as a stand-alone analyzer.

@@

\medskip\noindent\textbf{Other Tools }
%
We tried to compare \whoop with other similar approaches (see \S\ref{related}). However, we found this hard to achieve, as some tools are not freely available, while others are outdated for several years and are not working on the 4.0 Linux drivers.
